Use and acquisition of causal information for decision making under uncertainty

### 2018-05-10 Segundo_Semestre/CausalML_Workshop/Extended_Abstract.tex
cambios related work

In a bandit problem (\cite{sutton1998reinforcement}) an agent chooses an \textit{arm} from a slot machine, observes a reward and then moves on to the next machine wich is of the same kind and whose initial settings are independent of the previous machine and action.

@@

\cite{lattimoreNIPS2016} is, up to our current knowledge, the first paper to consider causal relations between the effects of actions. They consider a decision maker who must choose the best among several possible interventions on a given, and fully known, causal model. The optimality of the action in this context is in terms of the minimal regret. The case where the causal model is not known is left as future work.

\cite{sen2017identifying} extend the work of \cite{lattimoreNIPS2016} by considering a causal model partially known and intervening variables from the unknown part and by avoiding sampling arms that are considered sub-optimal.

>>>>

In a bandit problem an agent chooses an \textit{arm} from a slot machine, observes a reward and then moves on to the next machine wich is of the same kind and whose initial settings are independent of the previous machine and action \cite{sutton1998reinforcement} .

@@

Up to our current knowledge \cite{lattimoreNIPS2016} is the first paper to consider causal relations between the effects of actions. They consider a decision maker who must choose the best among several possible interventions on a given, and fully known, causal model. The optimality of the action in this context is in terms of the minimal regret. The case where the causal model is not known is left as future work.

By considering a causal model which is partially known and intervening variables from the unknown part and by avoiding sampling arms that are considered sub-optimal \cite{sen2017identifying} extend the work of \cite{lattimoreNIPS2016}.
